---
title: "Data Visualization Step Two"
description: |
categories:
  - Education Techonology
author:
  - name: Michelle Cui
date: 2025-03-06
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

### Research Question 1
What is the relationship between teacher’s perspectives on the school’s attitude toward using ICT technology in the classroom?\
(This question aims to explore institutional attitude toward information and communication technology (ICT) influence individual teacher behavior in adopting technology in the classroom).\

**Variable selection: **
it2g06a: ICT use at school when teaching
IT2G14A: Your School/Use of ICT in teaching at your school/ICT is considered a priority for use in teaching – X-axis
cntry: Country(Denmark, Finland, and Uruguay)
partt: Survey participation
idteach: Teacher ID\

```{r message = FALSE, warning = FALSE, include=FALSE}
library(here)
library(rio)
library(tidyverse)
library(tidyr)
library(janitor)
library(haven)
library(dplyr)
library(gt)
library(colorblindr)
theme_set(theme_minimal(base_family = "Times"))
library(kableExtra)
library(patchwork)
library(modelsummary)
library(car)
library(lme4)

```

```{r}
# read in data
load(here("data","MERGEDTP.Rdata"))
mergedtp <- MERGEDTP
```

```{r}
rq1_data <- mergedtp %>% 
  clean_names() %>% 
  select(idteach, cntry, partt, year, it2g06a, it2g14a) %>% 
  filter(partt == 1)

rq1_data <- na.omit(rq1_data)

rq1_data$it2g14a <- factor(rq1_data$it2g14a,
                           levels = c(1,2,3,4),
                           labels = c("Strongly Agree", "Agree", "Disagree", "Strongly Disagree"))

rq1_data$it2g06a <- factor(rq1_data$it2g06a,
                           levels = 1:5,
                           labels = c("Never", "Less than once a month", "At least once a month but not every week", "At least once a week but not every day", "Every day"))

datasummary_skim(rq1_data, 
                 type = "categorical")

```

The summary table looks good so far, but we can make it better by integrating table-making packages. At here, I added output = "gt" to apply the gt function to the rest of the table. However, the summary is still too robust.\


```{r}
rq1_summary <- rq1_data %>% 
  datasummary_skim(type = "categorical", output = "gt") %>% 
  tab_header(
    title = "Summary of Teachers' ICT Perspectives (2018 & 2020)"
  ) %>% 
  cols_width(everything() ~ px(200)) %>% 
  opt_table_outline()
rq1_summary
```

Therefore, I decided to subgroup the dataset by country and year to show the counts and percentage for each category.\

```{r}
rq1_summary <- rq1_data %>% 
  group_by(cntry, year, it2g06a, it2g14a) %>% 
  summarise(
    N = n(), .groups = "drop") %>% 
  mutate(Percent = round(100 * N/sum(N), 1)) %>% 
  pivot_wider(names_from = year, values_from = c(N, Percent), names_glue = "{year}_{.value}") %>% 
  arrange(cntry, it2g06a, it2g14a)

rq1_summary %>% 
  gt() %>% 
  tab_header(title = "Teachers' ICT perspectives by country and year (2018 & 2020)") %>% 
  cols_label(
    cntry = "Country",
    it2g06a = "ICT Use Frequency",
    it2g14a = "School ICT Priority",
    `2018_N` = "N (2018)",
    `2018_Percent` = "% (2018)",
    `2020_N` = "N (2020)",
    `2020_Percent` = "% (2020)"
  ) %>% 
  fmt_number(columns = c(`2018_Percent`, `2020_Percent`), decimals = 1) %>%
  tab_options(table.width = px(900)) %>% 
  tab_style(
    style = list(cell_fill(color = "#9EDBDB")),
    location = list(
      cells_body(columns = everything(), rows = it2g06a == "Every day"))
  ) %>% 
  tab_footnote(
    footnote = "Note: DNK refers to Denmark, FIN refers to Finland, and URY refers to Uruguay.")

```

Here is how I visualize the categorical data.\

```{r}
rq1_p1 <- ggplot(rq1_data, aes(x = it2g14a, fill = it2g06a)) +
  geom_bar(position = "fill") +
  facet_wrap(year ~ cntry) +
  labs(
    title = "Teacher ICT Use in Teaching by School ICT Priority",
    x = "School ICT Priority",
    y = "Propportion",
    fill = "Teacher ICT Use Frequency in Teaching"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

rq1_p1
```

The plot one looks good so far, but it is a bit busy, and the color looks too bright. So I changed the position to dodge in geom_bar, and applied scale_fill_OkabeIto() to make it color-blind friendly.\

```{r}
rq1_p2 <- ggplot(rq1_data, aes(x = it2g06a, fill = it2g14a)) +
  geom_bar(position = "dodge") +
  facet_wrap(year ~ cntry) +
  labs(
    title = "Relationship between Teacher ICT Use and Schools' perspective on ICT",
    fill = "School ICT Priority",
    y = "Propportion",
    x = "Teacher ICT Use Frequency in Teaching"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_OkabeIto()

rq1_p2
```


```{r}
rq1_data$year <- as.factor(rq1_data$year)

rq1_p3 <- rq1_data %>% 
  group_by(year, cntry, it2g06a,it2g14a) %>% 
  summarise(count = n(), .groups = "drop") %>% 
  ggplot(aes(x = year,
         y = count,
         group = interaction(cntry,it2g14a),
         color = it2g14a,
         linetype = cntry,
         shape = cntry))+
  geom_line() +
  geom_point(size = 2) +
  facet_grid(~ it2g06a) +
  labs(title = "Figure 1. ICT Use Across Countries (2018 & 2020)",
       x = "Year of Response",
       y = "Count",
       color = "School ICT Priority",
       linetype = "Country",
       shape = "Country"
  ) +
  scale_color_OkabeIto() +
  scale_shape_manual(values = c("DNK" = 0, "FIN" = 15, "URY" = 5))+
  theme(panel.spacing = unit(1, "lines"))

rq1_p3
```




