---
title: "Michelle Cui's Final Project"
description: |
  This is a blog where I am building up my work for EDLD 652 Data Visualization Final Project. The dataset I am looking at is the International Computer and Information Literacy Study (ICILS) Teacher Panel 2020. The dataset was retrieved from the International Association for the Evaluation of Educational Achievement (IEA) that is the host orgranization of ICILS. Here is more information about the study and report: [Data](https://www.iea.nl/data-tools/repository/icils),  [ICILS](https://nces.ed.gov/surveys/icils/), [Report: Changes in Digital Learning During a Pandemic—Findings From the ICILS](https://www.iea.nl/publications/study-reports/international-reports-iea-studies/changes-digital-learning-during Teacher Panel)
categories:
  - Education Techonology
author:
  - name: Michelle Cui
date: 2025-02-19
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r message = FALSE, warning = FALSE, include=FALSE}
library(here)
library(rio)
library(tidyverse)
library(janitor)
library(haven)
library(dplyr)
library(gt)
library(kableExtra)
library(scales)
library(colorblindr)
library(patchwork)
library(modelsummary)
library(car)
library(plotly) # adds some interactivity to the plot
theme_set(theme_minimal(base_family = "Times"))
```

```{r include=FALSE, message=FALSE}
load(here("data","MERGEDTP.Rdata"))
mergedtp <- MERGEDTP
```

#### Research question one

```{r message=FALSE, warning=FALSE, include=FALSE}
rq1 <- mergedtp %>% 
  clean_names() %>% 
  select(idteach,cntry,year,partt,it2g14a,it2g05a, it2g05b, ii2g12a)

sum(is.na(rq1))
colSums(is.na(rq1))

rq1_clean <- rq1 %>% 
  filter(!is.na(idteach) &!is.na(partt))

```

Summarize data for research question 1

```{r}
# Summary statistics
rq1_clean$it2g14a <- factor(rq1_clean$it2g14a,
                            levels = c(1,2,3,4),
                            labels = c("Strongly agree",
                                       "Agree",
                                       "Disagree",
                                       "Strongly disagree"))

rq1_clean$it2g05a <- factor(rq1_clean$it2g05a,
                            levels = c(1,2,3,4),
                            labels = c("Never", "Less than two years", "Between two and five years", "More than five years"))

rq1_clean$it2g05b <- factor(rq1_clean$it2g05b,
                            levels = c(1,2,3,4),
                            labels = c("Never", "Less than two years", "Between two and five years", "More than five years"))

rq1_clean$ii2g12a <- factor(rq1_clean$ii2g12a,
                            levels = c(1,2),
                            labels = c("Yes", "No"))

rq1_clean$partt <- factor(rq1_clean$partt,
                          levels = c(1,2,3),
                          labels = c("Both Cycles",
                                   "Only 2018",
                                   "Only 2020"))

rq1_clean <- rq1_clean %>% 
   rename(`Country ID` = cntry,
         `Year of Response` = year,
         `Teacher Participation` = partt,
         `School Consider ICT a Priority` =it2g14a,
         `ICT Use During Lesson` = it2g05a,
         `ICT Prepare Before Lesson` = it2g05b,
         `ICT Self-support` = ii2g12a)

```

A descriptive table for table 1

```{r}
datasummary_skim(rq1_clean,
                 type = "categorical",
                 title = "Table 1. Summary of School and Teacher's Perspective on ICT",
                 notes = "Source: International Computer and Information Literacy Study(ICILS)")
```

Missing Values:

Missing value

```{r message=FALSE, warning=FALSE, include=FALSE}
rq1_missing <- rq1_clean %>% 
  select(-idteach) %>% 
  group_by(`Year of Response`, `Teacher Participation`, `Country ID`) %>% 
  summarise(across(everything(), ~sum(is.na(.))), .groups = "drop")


rq1_table_missing <- rq1_missing %>% 
  gt() %>% 
  tab_spanner(
    label = "Missing Values by Year and Participation Cycle",
    columns = c(`Year of Response`, `Teacher Participation`)
  ) %>% 
  tab_header(
    title = "Table 2. Missing values in key ICT related variables",
    subtitle = "Insights into digital infrastructure and support disparities"
  ) %>% 
  cols_label(
    `Teacher Participation` = "Teacher Participation Cycle",
    `Country ID` = "Country",
    `Year of Response` = "Response Year"
  )
```

```{r}
rq1_table_missing
```

QR1: Visualization
Initial version:

```{r}
rq1_clean_vis <- rq1_clean %>% 
  filter(!is.na(`School Consider ICT a Priority`) &!is.na(`ICT Use During Lesson`) & !is.na(`ICT Prepare Before Lesson`) &!is.na(`ICT Self-support`)) %>% 
  filter(`Teacher Participation` == "Both Cycles")

p1 <- ggplot(data = rq1_clean_vis, aes(x = `ICT Use During Lesson`, fill= `School Consider ICT a Priority`)) +
  geom_bar(position = "dodge")+
  facet_wrap(`Year of Response`~ `Country ID`)+
  labs(title = "Figure 1. Frequency of ICT Use during lessons by School ICT Priority across countries",
       x = "ICT Use During Lessons",
       y = "Count",
       fill = "School ICT Priority")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_OkabeIto()

p1
```

RQ1: Visualization second version
Combining the two plots could provide a more comprehensive view of how ICT use evolved across different contexts before and during lessons, while also showing school ICT priority changes from 2018 to 2020.
By this point, I realize my data for Research Question one is not tidy enough.

```{r}

rq1_clean_vis_long <- rq1_clean_vis %>% 
  pivot_longer(cols = c(`ICT Use During Lesson`, `ICT Prepare Before Lesson`),
               names_to = "ICT Use",
               values_to = "ICT Frequency")

rq1_clean_vis_long$`Year of Response` <- as.factor(rq1_clean_vis_long$`Year of Response`)

p2 <- rq1_clean_vis_long %>% 
  ggplot(aes(x = `Year of Response`,
             group = interaction(`Country ID`, `School Consider ICT a Priority`),
             color = `School Consider ICT a Priority`,
             shape = `Country ID`)) +
  geom_line(stat = "count") +
  geom_point(stat = "count", size = 3) +
  facet_wrap(~ `Country ID`) +
  labs(title = "Figure 1. Frequency of ICT Use Before Lessons by School ICT Priority Across Countries (Pre- vs. Post-Pandemic)",
       x = "Year of Response",
       y = "Count",
       color = "School ICT Priority",
       linetype = "Country",
       shape = "Country") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_OkabeIto()

p2
```

My null hypothesis for research question one:
School ICT Priority has no influence on teacher's ICT use before and during lessons.

Run ANCOVA analysis to test my null hypothesis.

```{r}
rq1_analysis <- rq1 %>% 
  filter(!is.na(idteach) &!is.na(partt) &!is.na(it2g14a) &!is.na(it2g05a)&!is.na(it2g05b)&!is.na(ii2g12a)) %>% rename(`Country ID` = cntry,
         `Year of Response` = year,
         `Teacher Participation` = partt,
         `School Consider ICT a Priority` =it2g14a,
         `ICT Use During Lesson` = it2g05a,
         `ICT Prepare Before Lesson` = it2g05b,
         `ICT Self-support` = ii2g12a) %>% 
  filter(`Teacher Participation` == 3)

ancova_fit1 <- aov(`ICT Use During Lesson` ~ `School Consider ICT a Priority` + `Year of Response` + `Country ID` + `ICT Self-support`, data = rq1_analysis)
summary(ancova_fit1)

ancova_fit2 <- aov(`ICT Prepare Before Lesson` ~ `School Consider ICT a Priority` + `Year of Response` + `Country ID` + `ICT Self-support`, data = rq1_analysis)
summary(ancova_fit2)

```